Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-06 treestats_paper.tex
Attempt to streamline def'n of polarised node stat.

\paragraph{Polarisation}
In this definition we have associated with each node the summary of both the weight below the node
\emph{and} the weight not below the node.
Would it not be more natural to only include the first term, $f(\nw_{T_k}(u))$?
The reason for this definition is that it does not depend on the location of the root of the tree,
which in practice may be unknown.
Statistics of genotype sequence defined below in an analogous way
will not depend on knowledge of which allele is ancestral, i.e., on \emph{polarisation} of alleles.
For this reason, the node statistic above is the \emph{unpolarised} version,
while a \emph{polarised} node statistic is defined without the second term:
\begin{align}
    \text{(polarised)} \qquad
    \nodep(f, \iw)_u
    =
    \frac{1}{L} \sum_{k=1}^{n(\treeseq)} L_k f(\nw_{T_k}(u)) .
\end{align}

>>>>

\paragraph{Polarisation}
The node statistic defined above is appropriate for statistics such as nucleotide diversity, which is a function
of all alleles at given variable site.  For other statistics, one is only concerned with the derived state(s)
at a site, and we may defined a \emph{polarised} node statistic without the second term from our previous definition:

\begin{align}
    \text{(polarised)} \qquad
    \nodep(f, \iw)_u
    =
    \frac{1}{L} \sum_{k=1}^{n(\treeseq)} L_k f(\nw_{T_k}(u)) .
\end{align}
